Deciding to Disclose: A Decision Theoretic Agent Model of Pregnancy and Alcohol Misuse

### 2014-12-31 Background.tex
PDF figures

This section presents a brief overview of previous research, addressing in turn signalling games, normative decision theory, heuristic decision making, and descriptive decision theory.

>>>>

This section presents a brief overview of previous work relating to the theoretical backdrop to this approach, addressing in turn signalling games, normative decision theory, heuristic decision making, and descriptive decision theory.

### 2014-12-31 Methods.tex
PDF figures

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving then free parameters which were treated as uniformly distributed in the range given. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

>>>>

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of parameters given in table \ref{tab:sa_params}, giving eleven free parameters which were treated as uniformly distributed in the range given. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each, with emulator quality assessed by leave-one-out cross validation. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

### 2014-12-31 Model.tex
PDF figures

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=0.43\paperwidth]{figures/rounded_clover_infosets}
\end{adjustbox}
\caption{Simplified game tree.}

@@

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=0.43\paperwidth]{figures/tree_zoom}
\end{adjustbox}
\caption{Detail view of a single game tree branch.}

@@

%Might belong in a more methody bit? Read some stuff to check..
Women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)). They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly using the rules described in section \ref{sub:the_agents}.

@@

Formally then, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Additionally define a utility function \(u_{i}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), and distributions over types \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\).

@@

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogenous beliefs about  women and assume to some extent that they are honest.
Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible at least once, with exactly \(k\) encounters overall.

@@

Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution, which maps to \(u_{w}\) - i.e. \(s_{w}\) is a choice between simple lotteries. The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).

@@

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff based rule relys on a belief structure relating actions directly to rewards. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes. This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

>>>>

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=\textwidth]{figures/rounded_clover_infosets}
\end{adjustbox}
\caption{Simplified game tree. Green, blue, and orange arrows correspond to moves by nature, women, and midwives, respectively. Green terminal nodes indicate that the game may repeat from that point, and black nodes are exits.}

@@

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=0.43\paperwidth]{figures/tree_zoom}
\end{adjustbox}
\caption{Detail view of a single game tree branch, showing the possible moves by each player, with information sets for midwives.}

@@

%Might belong in a more methody bit? Read some stuff to check..
To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Additionally define two utility functions \(u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}\), \(u_{m}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}}\), with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}; and distributions over types \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\).

As noted, rather than solve the game, we allow populations of agents to play it, and hence stipulate further that women are drawn in order from a queue of \(n_{w}\) women (where \(n_{w}=1000\) in all simulations), and play against a midwife chosen at random from a population of \(n_{m}\) (\(n_{m}=100\)). They play for a maximum of \(r_{w}\) rounds (\(r_{w}=12\) following the routine number of ante-natal appointments in the UK \citep{NICE2010a}) or until they are referred, and a new player is drawn from the same distribution that produced the original players to replace them. If they are not referred, they rejoin the back of the queue after their appointment. In either case, they are informed of their payoff after each round and update their beliefs accordingly using the rules described in section \ref{sub:the_agents}.

@@

@@

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogenous beliefs about  women and assume to some extent that they are honest.
Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible for their type at least once, with exactly \(k\) encounters overall.

@@

Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e. \(s_{w}\) is a choice between simple lotteries. The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).

@@

Because of their differing problem representations, the simple payoff reasoners and their more complex counterparts incorporate this exogenous information differently. The simple payoff based rule relys on a belief structure relating actions directly to rewards which is essentially model free. Because payoffs differ by the agent's private type, the information shared may not correspond to the experience of the listening agent in the same scenario. As a result, payoff reasoners have a belief bias towards the most common player type, and can believe in outcomes that are, for them, impossible.

By contrast, representing the problem in terms of the probabilities of the individual lotteries imposes a model that abstracts the new information from payoffs, and allows the agent to discard implausible outcomes. This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.

### 2014-12-31 Results.tex
PDF figures

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Honest signalling\label{fig:honest_sharing}]{\includegraphics[width=0.43\paperwidth]{figures/honesty_sharing}

}\subfloat[Referrals\label{fig:ref_sharing}]{\includegraphics[width=0.43\paperwidth]{figures/ref_sharing}}\end{adjustbox}
\caption{Impact of information sharing on qualitative trends after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
\label{fig:sharing_trends}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/sharing_emulated_simulated}\end{adjustbox}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
\label{fig:outcome_plots}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\includegraphics[width=0.8\linewidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
\label{fig:emulated_sharing_iqr}
\end{figure}

@@

For the \ac{CPT}, and Bayesian decision models, the interaction of bias towards honesty, and distinction between payoffs has a significant, and non-linear effect on instability, and separability of groups. Figure \ref{fig:emulated_payoff_group_iqr} shows the effects, and also highlights the tendency towards poor separability of groups for both the heuristic type decision rules. The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule. Figure \ref{fig:emulated_payoff_group_iqr} shows better separation close to partial pooling at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.  For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling occurs.  The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).

>>>>

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=0.8\textwidth]{figures/honesty_sharing}
\end{adjustbox}
\caption{Impact of information sharing on trends in honest signalling after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
\label{fig:honest_sharing}
\end{figure}

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=0.8\textwidth]{figures/ref_sharing}
\end{adjustbox}
\caption{Impact of information sharing on referral trends after 1000 rounds, mean with 95\% confidence interval over 100 runs.}
\label{fig:ref_sharing}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\includegraphics[width=0.8\textwidth]{figures/sharing_emulated_simulated}\end{adjustbox}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules.}
\label{fig:outcome_plots}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\includegraphics[width=0.8\textwidth]{figures/unfixed_emu_sig_iqr}\end{adjustbox}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\).}
\label{fig:emulated_sharing_iqr}
\end{figure}

@@

For the \ac{CPT}, and Bayesian decision models, the interaction of bias towards honesty, and distinction between payoffs has a significant, and non-linear effect on instability, and separability of groups. Figure \ref{fig:emulated_payoff_group_iqr} shows the effects, and also highlights the tendency towards poor separability of groups for both the heuristic type decision rules. The response surface of the Bayesian payoff rule is slightly more nuanced than the simple Lexicographic rule. Figure \ref{fig:emulated_payoff_group_iqr} shows better separation, close to partial pooling\footnote{Pooling occurs when signallers of different types `pool' their signals, and one adopts the signals of another.} at high payoff distinction, with relatively modest honesty bias, which is reflected by the variance contributions of 11\% and 8\% respectively.  For the more complex rules, the general tendency is towards less pooling for higher values of both, but with pockets where full pooling\footnote{Indicating that all signallers types are using a single signal.} occurs.  The plots also suggest that the sensitivity of the \ac{CPT} rule is marginally greater, which is supported by the significant contribution to variance of close to 15\% for all measures of \(x_{h}\).
